---
title: "Using the sendis package"
author: "F. Michel-Sendis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette 
vignette: >
  %\VignetteIndexEntry{sendis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(sendis)
library(dplyr)

```
 
## Installation 

To use the `sendis` package you will need a working version of the [R software](https://www.r-project.org/). 

```{r, installation, message=FALSE, eval=FALSE}
# First time installation in the R console : 
# Download and load the devtools package
install.packages("devtools")
library(devtools)

# Install and load the development version from GitHub:
devtools::install_github("fmichelsendis/sendis")
library(sendis)
```


 

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
df<-filter(sendis, INST=="NEA", VER!="2.2")
plot_cumulchi(df)

```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
