---
title: "Using the sendis package"
author: "F. Michel-Sendis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette 
vignette: >
  %\VignetteIndexEntry{sendis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
 
library(dplyr)

```
 
## Installation 

To use the `sendis` package you will need a working version of the [R software](https://www.r-project.org/). 

```{r, installation, message=FALSE, eval=FALSE}
# First time installation in the R console : 
# Download and load the devtools package
install.packages("devtools")
library(devtools)

# Install and load the development version from GitHub:
devtools::install_github("fmichelsendis/sendis")
library(sendis)
```


 ## Some Definitions

We use the term *benchmarking suite* to refer to the list of $N$ different ICSBEP evaluations used by institutions. The selection of benchmarks differs from institution to institution.

* $k_c$: calculated multiplication factor;
* $\sigma_c$: statistical error of calculation
* $k_e$: experimentally measured (benchmark value) multiplication factor
* $\sigma_e$ experimental uncertainty around benchmark value
* 'Delta' : $\Delta = k_c - k_e$
* 'Residual' : $R=\frac{\Delta}{\sigma_e}$
* $\chi^2 = \frac{1}{N}\sum_i^N \frac{(k_c - k_e)^2}{\sigma_c^2 + \sigma_e^2}$

 
All experimental benchmark values and related physical parameters are public data and have been exported from the OECD NEA DICE database, 2016 edition. 


The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
data(sendis)
df<-filter(sendis, INST=="NEA", VER!="2.2")
sendis::plot_cumulchi(df)

```
 
