---
title: "Import your data"
author: "F. Michel-Sendis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Import your data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  echo=FALSE, 
  message=FALSE, 
  warning=FALSE, 
  eval=TRUE,
  fig.align='center'
  #fig.width = 100pct
  ) 

htmltools::tagList(rmarkdown::html_dependency_font_awesome())

library(dplyr)
library(plotly) 

```

<link rel="stylesheet" href="https://use.fontawesome.com/releases/v5.6.3/css/all.css" integrity="sha384-UHRtZLI+pbxtHCWp1t77Bi1L4ZtiqrqD80Kn4Z8NTSRyMA2Fd33n5dQ8lWUE00s/" crossorigin="anonymous">


The **sendis** package was created with the aim to facilitate the import of new data. In general, if you are into criticality calculations, the first thing you will want to do is to see how other people's results compare to *your* calculated data. Here are the instructions to do so. 



## CSV template 

You can import your own data provided it is in 
[this csv template](../files/sendis_template.csv). This template is designed to be the ouput of a criticality benchmark calculation : each **observation** (e.g. one benchmark result per row) has **7 features** or variables (in columns). This is the format that the [calcs](reference/calcs.html) dataset follows. Below is an example of what your csv file structure should look like before it can be imported. 

<br> 

```{r, fig.show='hold', fig.align='center'}
library(sendis)
library(kableExtra)
set.seed(137)
# sample n random entries from calcs : 
df<-calcs
n<-20
df<-df[sample(nrow(df), n), ]
rownames(df)<-NULL
df<-df%>%mutate(CODE="MYCODE",INST="MYLAB")
knitr::kable(df)%>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
 
```

## Format and description of variables 

  * `FULLID` : `[character]` **ICSBEP** evaluation identifier, in the format FISS-FORM-SPEC-CASE-SUBCASE;
  * `MODEL` : `[character]` model input used, when specified, otherwise leave blank;  
  * `CALCVAL` : `[numerical]`, calculated value of $k_{e\!f\!f}$;
  * `CALCERR` : `[numerical]`, statistical uncertainty on $k_{e\!f\!f}$; 
  * `INST` : `[character]` used to identify institute or author of calculation
  * `CODE` : `[character]` name of the code used;
  * `LIBVER` : `[character]` library used, in the format LIB-VER (e.g.: JEFF-3.3)
 
**Note** the format for the two categorical values `FULLID` and `LIBVER` is extremely important, as these columns are parsed and split at the hyphen ('-') into separate variables. 

## Importing into `sendis`

The function `sendis::import_submissions()` imports all `*.csv` files in the directory specified as its argument `path`. This function will fail with an error if your csv files are not in the [csv template](../files/sendis_template.csv) that is required. 


```{r, import-user-data, echo=TRUE, eval=TRUE}
# use function import_submission(path="yourfolder")
df<-import_submissions(path = "../docs/files/mycsvfiles/")

# verify import by checking the dimensions of dataframe `mydata`: 
dim(df)

# dataframe contains all of your csv data in `yourfolder/` :
head(df)
```

Your data is imported but not yet in the format of the `sendis` dataframe. You only need to call function `compile_to_sendis()` in order to do so : 

```{r, compile-user-data, echo=TRUE, eval=TRUE}
# merge your dataframe and bind it to the sendis dataframe
mydata<-compile_to_sendis(df)

# verify import by checking the new dimensions of dataframe `mydata`: 
dim(mydata)
dim(sendis)
```

Try plotting it :

```{r, plot-user-data,echo=TRUE, eval=TRUE}
plot_afge(mydata)
```






## Contribute your data 

Submit your calculated results to be included as part of the  `calcs` and `sendis` datasets of the package


 